---
title: "sparklyr Pipeline"
output: github_document
---

## Install `sparklyr` from a branch

Use the `feature/ml-pipeline` branch to access the new pipeline features
```{r}
devtools::install_github("rstudio/sparklyr")
```

## Open a local `sparklyr` connection

```{r}
library(sparklyr)
sc <- spark_connect(master = "local")
```

## Copy mtcars and split them for test and training

```{r}
spark_mtcars <- sdf_copy_to(sc, mtcars, overwrite = TRUE) %>%
 sdf_partition(training = 0.4, testing = 0.6)
```


## Create the pipeline

Create a new `ml_pipeline()` object, and pass each step as an argument.  The result is a 3 stage pipeline. 
```{r}

my_pipeline <- ml_pipeline(sc) %>%
  ft_binarizer("mpg", "guzzler", 20) %>%
  ft_r_formula(guzzler ~ wt + cyl) %>%
  ml_logistic_regression()

my_pipeline
```


## Train the model

Use `ml_fit()` to train the model, and save the results to the `model` variable.  
```{r}
model <- ml_fit(my_pipeline, spark_mtcars$training)

model
```

## Evaluate the model

`ml_transform()` would be the equivalent of a `predict()` function.  The command is basically saying take the `spark_mtcars$testing` dataset and "transform" it using this pipeline, which happens to have a modeling step at the end.

```{r}
predictions <- ml_transform(x = model, 
                            dataset = spark_mtcars$testing)


dplyr::glimpse(predictions)
```

```{r}

predictions %>%
  dplyr::group_by(guzzler, prediction) %>%
  dplyr::tally()
```

## Save the model

The model can be saved to disk using `ml_save`.
```{r}
ml_save(model, "new_model", overwrite = TRUE)
```

The saved model retains the transformation stages
```{r}
list.files("new_model")
spark_disconnect(sc)
```

## Reload the model

We will use a new connection to confirm that the model can be reloaded

```{r}
library(sparklyr)
sc <- spark_connect(master = "local")
```

Use `ml_load()` to read the saved model

```{r}
spark_mtcars <- sdf_copy_to(sc, mtcars, overwrite = TRUE) 

reload <- ml_load(sc, "new_model")

reload
```


```{r}
reload_predictions <- ml_transform(x = reload, 
                            dataset = spark_mtcars)

dplyr::glimpse(reload_predictions)
```

```{r}
spark_disconnect(sc)
```
